Full 18s Community composition

### 2019-10-30 code/whole_18s_community_compare.Rmd
updated relative abundance plot

View plot of UniFrac NMDS
```{r, echo=F}
unifrac_plot_data <- mono %>%
  scores() %>%
  as_tibble(rownames = "sample_id") %>%
  left_join(field, by="sample_id")

@@

```{r, echo=F, fig.height=8, fig.width=10}
p <- ra %>% 
  left_join(assign, by="asv_id") %>% 
  group_by(phylum, sample_id) %>% 
  summarise(rel_abund = sum(rel_abund)) %>% 
  ungroup() %>% 
  left_join(field, by="sample_id") %>% 
  select(sample_id, phylum, rel_abund, date, elev_m) %>% 
  arrange(sample_id)

ggplot(p, aes(x=phylum, y=sample_id %>% fct_reorder(elev_m))) +
  geom_point(aes(color = phylum, size = rel_abund), alpha=0.7) +
  scale_size(range = c(1, 10)) +
  ylab("Sample ID") +
  xlab("OTU") +
  labs(fill = "OTU", alpha="Relative abundance", title = "Relative abundance plot of 18S phyla ") +
  scale_x_discrete(position = "bottom") +
  theme(axis.text.x = element_text(hjust=1,angle=45)) +
  scale_colour_discrete(guide = FALSE) # turn off legend
```

@@

<br>
<br>
Table zoom in on the most abundance phyla

>>>>

```{r unifrac_nmds, echo=F}
unifrac_plot_data <- mono %>%
  scores() %>%
  as_tibble(rownames = "sample_id") %>%
  left_join(field, by="sample_id")

@@

```{r set_plot, echo=F}
p <- ra %>% 
  left_join(assign, by="asv_id") %>% 
  group_by(phylum, sample_id) %>% 
  summarise(rel_abund = sum(rel_abund)) %>% 
  ungroup() %>% 
  left_join(field, by="sample_id") %>% 
  select(sample_id, phylum, rel_abund, date, elev_m) %>% 
  arrange(sample_id) %>% 
  filter(rel_abund >= 0.01) # only show phyla with >= 1% rel abund

# ggplot(p, aes(x=phylum, y=sample_id %>% fct_reorder(elev_m))) +
#   geom_point(aes(color = phylum, size = rel_abund), alpha=0.7) +
#   scale_size(range = c(1, 10)) +
#   ylab("Sample ID") +
#   xlab("OTU") +
#   labs(fill = "OTU", alpha="Relative abundance", title = "Relative abundance plot of 18S phyla ") +
#   scale_x_discrete(position = "bottom") +
#   theme(axis.text.x = element_text(hjust=1,angle=45)) +
#   scale_colour_discrete(guide = FALSE) # turn off legend
```

```{r facet_bar, echo=F, fig.width=10}
cust_theme <- theme(legend.position = "none",
                    panel.grid.major.x = element_blank(), # remove vertical lines in background
                    panel.grid.minor.x = element_blank(),
                    axis.line=element_blank(), # remove x axis
                    axis.title.x=element_blank(), 
                    axis.text.x=element_blank(),
                    axis.ticks.x=element_blank(),
                    panel.spacing = unit(-0.01, "lines"), # remove space between facet panels
                    strip.text.x = element_text(angle = 90, hjust=1.0, vjust = 0.8), # rotate facet labels 90
                    strip.background = element_blank()) # remove grey boxes around facet labs

# order algae, fungi, protists, other
phylum_ord <- c("Chlorophyta_ph", "Ochrophyta","Basidiomycota", "Ascomycota", "Chytridiomycota", "Ciliophora","Cercozoa","Protalveolata", "Phragmoplastophyta")

ggplot(p, aes(x=sample_id %>% fct_reorder(elev_m), y=rel_abund)) +
  geom_bar(aes(fill=phylum), stat="identity") + # classic stacked relative abundance plot
  coord_flip() +
  facet_grid(~phylum %>% fct_relevel(phylum_ord), switch = "x") +
  labs(title = "Relative abundance plot of 18S phyla", x="Sample ID (from lowest to highest elevation)") +
  cust_theme
```

@@

<br>
<br>
